### 2018-09-26 latex/mst_lukkarila_juri_2017.tex
cleaned a little
cleaned

% Graphics package
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{pdfpagemode=UseNone, pdfstartview=FitH,
  colorlinks=true,urlcolor=red,linkcolor=blue,citecolor=black,
  pdftitle={Conversation Assistant},pdfauthor={Juri Lukkarila},
  pdfkeywords={speech recognition}}

% Extended equation and symbol functionality
\usepackage{amsfonts,amssymb,amsbsy}
\usepackage{amsmath}
\usepackage{bm}    % bold math \bm{math expression}

@@

% MATLAB formatting
\usepackage{mcode}		% matlab code highlighting

>>>>

% Graphics package
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{pdfpagemode=UseNone,
            pdfstartview=FitH,
            colorlinks=true,
            urlcolor=red,
            linkcolor=blue,
            citecolor=black,
            pdftitle={Conversation Assistant},
            pdfauthor={Juri Lukkarila},
            pdfkeywords={speech recognition}}

% Extended equation and symbol functionality
\usepackage{amsfonts,amssymb,amsbsy,amsmath}

% bold math \bm{math expression}
\usepackage{bm}

@@

% matlab code highlighting
\usepackage{mcode}
